%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% And more modifications by:
% Drew Sabelhaus (apsabelhaus@cmu.edu)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%% 
% TO-DO
% TODO 
% Updates:
%	- remove from github public
%	- remove PII
%	- DNA actuators patent was granted
% 	- update/confirm presentations
%	- update under review and in prep

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4

% Some other packages:
\usepackage{etaremune}% enumerate in reverse. That's silly. Used for publications.
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{booktabs}

% Credit to... (insert here)
\newcommand\doilink[1]{\href{http://dx.doi.org/#1}{#1}}
\newcommand\doi[1]{doi:\doilink{#1}}
\newcommand\arxivlink[1]{\href{https://arxiv.org/abs/#1}{#1}}
\newcommand\arxiv[1]{arXiv:\arxivlink{#1}}
\usepackage{soul} % for better underline, \ul

% And for adjusting tables:
%\newcommand\Tstrut{\rule{0.1pt}{0.1cm}}
\newcommand\Tstrut{\rule{0pt}{2.6ex}}         % = `top' strut

\newcommand{\myname}{{\fontdescript{A.P. Sabelhaus}}}
\newcommand{\mername}{\underline{M.L. Anderson}}
\newcommand{\ranname}{\underline{R. Jing}}
\newcommand{\juanname}{\underline{J.C. Pacheco Garcia}}
\newcommand{\akuaname}{\underline{A. Dickson}}

\begin{document}

%-------------------------------------------------------------------------
%	TITLE SECTION
%------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\raggedright{ % left-align the heading
\namesection{Andrew P.}{Sabelhaus}{ % Your name
\urlstyle{same}\url{www.apsabelhaus.com} | 
\href{mailto:asabelha@bu.edu}{asabelha@bu.edu} | (617) 358-4500 | {\it he, him, his}}
}


%---------------------------------------------------------------------
% Professional Experience
%---------------------------------------------------------------------

% List my NASA stuff here - technically happened contemporanously but...
\vspace{0.2cm}
\section{\underline{Appointments}}

\vspace{0.2cm}

%% IC Postdoc

%{\fontdescript{Intelligence Community (IC) Postdoctoral Research Program \hfill Postdoctoral Fellow}}

%{\location{\hspace{0.3cm} Administered by Oak Ridge Institute for Science and Education (ORISE) \hfill 2020 - Present}}
%{\location{\hspace{0.3cm} Hosted at Carnegie Mellon University, Dept. of Mech. Eng. }}
%{\location{\hspace{0.3cm} Pittsburgh, PA}}

\fontsubsection{Assistant Professor}
\hfill % pushes the following line to the right side
\fontdescript{Boston University}

%{\fontdescript{Boston University \hfill Assistant Professor}}

{\location{\hspace{0.3cm} Department of Mechanical Engineering \hfill 2022 - Present}}
{\location{\hspace{0.3cm} Division of Systems Engineering \hfill 2022 - Present}}
{\location{\hspace{0.3cm} Center for Information Systems and Engineering \hfill 2022 - Present}}
%{\location{\hspace{0.3cm} PI, Soft Robotics Control Lab}}

\vspace{0.1cm}


\fontsubsection{Postdoctoral Research Fellow}
\hfill % pushes the following line to the right side
\fontdescript{Carnegie Mellon University}

{\location{\hspace{0.3cm} Deptartment of Mechanical Engineering \hfill 2019 - 2021}}
%{\location{\hspace{0.3cm} Soft Machines Lab ({\it{PI: Carmel Majidi}}) \hfill Pittsburgh, PA}}

\vspace{0.1cm}

%% NASA, through NSTRF

\fontsubsection{Visiting Technologist}
\hfill % pushes the following line to the right side
\fontdescript{NASA Ames Research Center}

{\location{\hspace{0.3cm} Intelligent Systems Division \hfill 2015 - 2019}}
%{\location{\hspace{0.3cm} Intelligent Robotics Group and Robust Software Engineering \hfill Moffet Field, CA}}

%{\location{\hspace{0.3cm} Intelligent Systems Division \hfill 2015 - 2019}}
%{\location{\hspace{0.3cm} Intelligent Robotics Group and Robust Software Engineering}}
%{\location{\hspace{0.3cm} Moffet Field, CA}}
%{\location{\hspace{0.3cm} Intelligent Robotics Group and Robust Software Engineering \hfill Moffet Field, CA}}

\vspace{0.1cm}

%% NASA and Berkeley, when I was on the NSF fellowship

%{{\fontdescript{University of California, Berkeley \hfill Graduate Research Fellow}}

\fontsubsection{Graduate Research Fellow}
\hfill % pushes the following line to the right side
\fontdescript{University of California, Berkeley}
  
{\location{\hspace{0.3cm} Department of Mechanical Engineering \hfill 2012-2019}}
%{\location{\hspace{0.3cm} Berkeley Emergent Space Tensegrities Lab ({\it{PI: Alice Agogino}}) \hfill Berkeley, CA}}

%{\location{\hspace{0.3cm} Dept. of Mechanical Engineering \hfill 2012-2019}}
%{\location{\hspace{0.3cm} Berkeley Emergent Space Tensegrities Lab ({\it{PI: Alice Agogino}})}}
%{\location{\hspace{0.3cm} Berkeley, CA}}

  
%------------------------------------------------
% Education
%------------------------------------------------

% I'm writing this out manually instead of using the nice section headers.
% TO-DO: make this into new commands to make easy.

\section{\underline{Education}}
\vspace{0.2cm}

%%%%%%%%%% PhD:

% First line: degree and school
\fontsubsection{Ph.D.  Mechanical Engineering}
\hfill % pushes the following line to the right side
\fontdescript{University of California, Berkeley}

% On the next line:
\fontlocation{Dissertation title: {\it Tensegrity Spines for Quadruped Robots}}
\hfill  %, have the date flush-right under the school name
\fontlocation{August 2019}

% Then, the committee members
{\fontlocation Dissertation Committee: {\it Alice M. Agogino (Chair), Andrew Packard, Claire Tomlin, Murat Arcak}}

% spacing for the next degree
%\sectionspace
\vspace{0.1cm}

%%%%%%%%%% Master's:

% First line: degree and school
\fontsubsection{M.S.  Mechanical Engineering}
\hfill % pushes the following line to the right side
\fontdescript{University of California, Berkeley}

% On the next line:
\fontlocation{Thesis: {\it Mechanism and Sensor Design for SUPERball, a Cable-Driven Tensegrity Robot}}
\hfill  %, have the date flush-right under the school name
\fontlocation{Dec. 2014}

% Then, the committee members
{\fontlocation Thesis Committee: {\it Alice M. Agogino, Dennis Lieu}}

% spacing for the next degree
%\sectionspace
\vspace{0.1cm}

%%%%%%%%%% Bachelor's:

% First line: degree and school
\fontsubsection{B.S.  Mechanical Engineering}
\hfill % pushes the following line to the right side
\fontdescript{University of Maryland, College Park}

% On the next line:
%\hspace{0.7cm} \fontsubsection{Minor: Computer Science}
{\fontlocation {\it Minor in Computer Science}}
\hfill  %, have the date flush-right under the school name
\fontlocation{May 2012}

% spacing for the next degree
%\sectionspace


%\sectionspace % Some whitespace after the section

%-----------------------------------------------------------------------
% Awards
%------------------------------------------------------------------------

% To-Do: have I helped win any other grants?
\vspace{0.2cm}
\section{\underline{Awards}}

\vspace{0.1cm}

%\sectionspace

{\fontsubsection{At Boston University}}

\begin{etaremune}[itemsep=0.05cm]

\setcounter{enumi}{11}

\item {{\fontdescript{NSF Faculty Early Career Development Program (CAREER) Award.}} National Science Foundation. 2024.}

\item {{\fontdescript{Outstanding Associate Editor.}} {\it IEEE International Conference on Robotics and Automation}, 2023.}

\end{etaremune}

\vspace{0.1cm}

{\fontsubsection{Before Joining Boston University}}

\begin{etaremune}[itemsep=0.05cm]

%\setcounter{enumi}{4}

\item {{\fontdescript{Intelligence Community Postdoctoral Research Fellowship.}} Office of the Director of National Intelligence. Title: {\it Rapid Deployment of Hard-to-Control Robots with Optimality Tradeoffs.} 2020-2022.}

\item {{\fontdescript{Outstanding Graduate Student Instructor Award.}} University of California, Berkeley. 2018.}

\item {{\fontdescript{NASA Space Technology Research Fellowship.}} National Aeronautics and Space Administration. Title: {\it Trajectory Tracking in Nonlinear, High-Order, Underactuated Robotic Systems.} 2015-2019.}
  
\item {{\fontdescript{Markowski-Leach Foundation Award.}} {\it Awarded to LGBTQ individuals at San Francisco Bay Area institutions who ``are likely to make a substantial contribution to society.''} 2013-2014, re-awarded 2016-2018.}

\item {{\fontdescript{NSF Graduate Research Fellowship.}} National Science Foundation. 2012-2015.}

\item {{\fontdescript{University Leadership Award.}} University of Maryland, College Park. 2012.}

\item {{\fontdescript{Office of LGBTQ Equity Award.}} University of Maryland, College Park. 2011.}

\item {{\fontdescript{President's Scholarship.}} University of Maryland, College Park. 2008.}

\end{etaremune}

%-----------------------------------------------------------------------
% Funding
%------------------------------------------------------------------------

\vspace{0.2cm}
\section{\underline{Funding}}

\vspace{0.1cm}

{{\fontdescript{Total amount of funding at Boston University:}}} \$1,835,205

{{\fontdescript{Personal share of funding at Boston University:}}} \$1,345,242

\vspace{0.3cm}

{\fontsubsection{At Boston University - PI}}

\begin{etaremune}[itemsep=0.05cm]

\setcounter{enumi}{6}

\item {{\fontdescript{NSF Foundational Research in Robotics (FRR).}} {\it CAREER: Safe Autonomy for Soft Robots.} 2024-2029.} (\$600,000.)

\item {{\fontdescript{Office of Naval Research (ONR).}} {\it Lightweight Soft Robotic Vehicles with Inflation-Based Locomotion.} 2024-2025.} (\$68,300.) PI: Sabelhaus, Co-PI: Xiaonan Huang, University of Michigan Ann Arbor.

\item {{\fontdescript{National Reconnaissance Office (NRO) Architecture After Next.}} {\it Soft Robot Proprioception with Space-Compatible Artificial Muscles.} 2023-2024.} (\$210,459.)

\end{etaremune}

\vspace{0.2cm}

{\fontsubsection{At Boston University - Co-PI}}

\begin{etaremune}[itemsep=0.05cm]

\item {{\fontdescript{NSF Dynamics, Control, and System Diagnostics (DCSD).}} {\it Koopman in the Field: Feedback, Teaching, and Adaptation for Real-World Mechanical Systems.} 2025-2027.} (\$522,592, personal share \$261,296.) PI: Roberto Tron (BU MechE), co-PI: Sabelhaus.

\item {{\fontdescript{NSF Cyberinfrastructure for Sustained Scientific Innovation (CSSI).}} {\it Collaborative Research: Elements: Discrete Simulation of Flexible Structures and Soft Robots.} 2022-2025.} (\$169,987 with \$35,200 REU Supplement Awards.) PI: M. Khalid Jawed (University of California Los Angeles), co-PIs: Sabelhaus, Carmel Majidi (Carnegie Mellon University).

\end{etaremune}


%-----------------------------------------------------------------------
% Research Productivity Statistics/Snapshot
%------------------------------------------------------------------------

\vspace{0.2cm}
\section{\underline{Publications}}
%\vspace{-0.3cm}
%Research Output Snapshot
 
%\renewcommand{\arraystretch}{1.2}
%\begin{tabularx}{1\textwidth}{ p{3cm} | p{3cm} | p{3cm} | X | X }
%\multicolumn{3}{ p{9cm} | }{ {\fontdescript{Peer-Reviewed Publication Count:}} } & {\fontdescript{Total Citations:}} & {\fontdescript{h-index:}} \\
%\hline
%						& 1st-Author or PI:\Tstrut 	& All: 	& \multirow{3}{*}{\huge 813*  (343$^\dag$) \Tstrut}	& \multirow{3}{*}{\huge 13*  (7$^\dag$) \Tstrut} \\
%Conference: \Tstrut	& \Large 7 					& \Large 12 			& 													&  \\
%Journal: 			& \Large 4					& \Large 9 			& 													& \\
%Total: 				& \Large 11 					& \Large 21			&													&
%\end{tabularx}

\renewcommand{\arraystretch}{1.2}
\begin{tabularx}{1\textwidth}{ p{3cm} | p{2cm} | p{2cm} | p{2cm} | X | X }
\multicolumn{4}{ p{9cm} | }{ {\fontdescript{Peer-Reviewed Publication Count:}} } & {\fontdescript{Total Citations:}} & {\fontdescript{h-index:}} \\
\hline
					& Conference:\Tstrut 	& Journal: 		& Total: 		& \multirow{3}{*}{\huge 1364*  (650$^\dag$) \Tstrut}	& \multirow{3}{*}{\huge 16*  (11$^\dag$) \Tstrut} \\
1st-Author or PI: \Tstrut	& \Large 10 			& \Large 5 		& \Large 15	&										&  \\
All: 					& \Large 15		& \Large 11 		& \Large 26	&										& \\
\end{tabularx}

% some explanations
\vspace{0.2cm}
{\small \it *Via Google Scholar, \href{https://scholar.google.com/citations?user=ze69yEMAAAAJ\&hl=en}{https://scholar.google.com/citations?user=ze69yEMAAAAJ\&hl=en}. \\
$^\dag$Via Web of Science, \href{https://www.webofscience.com/wos/author/record/1791313}{https://www.webofscience.com/wos/author/record/1791313}.}

%{\small \it *Google Scholar, \href{https://scholar.google.com/citations?user=ze69yEMAAAAJ}{https://scholar.google.com/citations?user=ze69yEMAAAAJ}. $^\dag$Web of Science, \href{https://www.webofscience.com/wos/author/record/1791313}{https://www.webofscience.com/wos/author/record/1791313.}

%-----------------------------------------------------------------------
% Publications - now split between journal and conference
%------------------------------------------------------------------------

\vspace{0.6cm}
{\fontsubsection{Journal Publications}}
\vspace{0.2cm}

\textit{Names of advised students/postdocs are underlined.}

% For the publication titles, I use the 'description' font from the class.
\begin{etaremune}[itemsep=0.1cm]

\item A. Choi, \ranname, \myname, M.K. Jawed, ``DisMech: A Discrete Differential Geometry-Based Physical Simulator for Soft Robots and Structures,'' {\it IEEE Robotics and Automation Letters}, Vol. 9, No. 4., Apr 2024. \doi{10.1109/LRA.2024.3365292}

\item \myname, Z. Patterson, A. Wertz, C. Majidi, ``Safe Supervisory Control of Soft Robot Actuators,'' {\it Soft Robotics}, Vol. 11, No. 4, Aug 2024. \doi{10.1089/soro.2022.0131}

\item X. Huang, Z.J. Patterson, \myname, W. Huang, K. Chin, Z. Ren, M.K. Jawed, C. Majidi, ``Design and Closed Loop Motion Planning of an Untethered Swimming Soft Robot using 2D Discrete Elastic Rods Simulations,'' {\it Advanced Intelligent Systems}, 2200163, Sept 2022. \doi{10.1002/aisy.202200163}


\item \myname, R.K. Mehta, A. Wertz, C. Majidi, ``In-Situ Sensing and Dynamics Predictions for Electrothermally-Actuated Soft Robot Limbs,'' {\it Frontiers in Robotics and AI}, Vol. 9, May 2022. \doi{10.3389/frobt.2022.888261}

\item M. Zadan, D.K. Patel, \myname, J.Liao, A. Wertz, L. Yao, C. Majidi, ``Liquid Crystal Elastomer with Integrated Soft Thermoelectrics for Shape Memory Actuation and Energy Harvesting,'' {\it Advanced Materials}, Vol. 34, No. 23, April 2022. \doi{10.1002/adma.202200857}

\item Z.J. Patterson, \myname, C. Majidi, ``Robust Control of a Multi-Axis Shape Memory Alloy-Driven Soft Manipulator,'' {\it IEEE Robotics and Automatics Letters}, Vol. 7, No. 2, April 2022. \doi{10.1109/LRA.2022.3143256}

\item \myname, K. Zampaglione, E. Tang, L.H. Chen, A.K. Agogino, A.M. Agogino, ``Double-Helix Linear Actuators.'' {\it Journal of Mechanical Design (ASME)}, Vol. 143, No. 10, Oct. 2021. \doi{10.1115/1.4050739}

\item Z. Ren, X. Huang, M. Zarepoor, \myname, C. Majidi, ``Shape Memory Alloy (SMA) Actuator with Embedded Liquid Metal Curvature Sensor for Closed-Loop Control." {\it Frontiers in Robotics and AI}, Vol. 8, Mar. 2021. \doi{10.3389/frobt.2021.599650}

\item \myname, H. Zhao, E. Zhu, A.K. Agogino, A.M. Agogino, ``Model-Predictive Control with Inverse Statics Optimization for Tensegrity Spine Robots.'' {\it IEEE Transactions on Control System Technology}, Vol. 29, No. 1, Jan. 2021. \doi{10.1109/TCST.2020.2975138}

\item \myname, A.H. Li, K.A. Sover, J. Madden, A. Barkan, A.K. Agogino, A.M. Agogino, ``Inverse Statics Optimization for Compound Tensegrity Robots.'' {\it IEEE Robotics and Automation Letters}, Vol. 5, No. 3, July 2020. \doi{10.1109/LRA.2020.2983699}

\item K. Caluwaerts, J. Despraz, A. Iscen, \myname, J. Bruce, B. Schrauwen, V. SunSpiral, ``Design and Control of Compliant Tensegrity Robots through Simulation and Hardware Validation.'' {\it Journal of the Royal Society Interface,} Vol. 11, No. 98, Sept. 2014. \doi{10.1098/rsif.2014.0520}

\end{etaremune}

%%%%%%%%% Conferences

%\vspace{0.2cm}
%\section{Conference Publications}
%\vspace{0.2cm}

\vspace{0.4cm}
{\fontsubsection{Conference Publications}}
\vspace{0.2cm}

\textit{Names of advised students/postdocs are underlined.}

% For the publication titles, I use the 'description' font from the class.
\begin{etaremune}[itemsep=0.1cm]

\item \akuaname, \juanname, \ranname, \mername, \myname, ``Real-Time Trajectory Generation for Soft Robot Manipulators Using Differrential Flatness,'' {\it IEEE International Conference on Soft Robotics (RoboSoft)}, Accepted for Publication, 2025. \doi{10.48550/arXiv.2412.08568}

\item \mername, \ranname, \juanname, I. Yang, S. Alizadeh-Shabdiz, C. DeLorey, \myname, ``Maximizing Consistent Force Output for Shape Memory Alloy Artificial Muscles in Soft Robots,'' {\it IEEE International Conference on Soft Robotics (RoboSoft)}, Apr. 2024. \doi{10.1109/RoboSoft60065.2024.10521983}

\item \juanname, \ranname, \mername, M. Ianus-Valdivia, \myname, ``A Comparison of Mechanics Simplifications in Pose Estinmation for Thermally-Actuated Soft Robot Limbs.'' {\it ASME 2023 Conference on Smart Materials, Adaptive Structures, and Intelligent Systems (SMASIS)}, Sept. 2023. \doi{10.1115/SMASIS2023-110774}

\item A. Wertz*, \myname*, C. Majidi, ``Trajectory Optimization for Thermally-Actuated Soft Planar Robot Limbs,'' {\it IEEE International Conference on Soft Robotics (RoboSoft)}, April 2022. *Equal Contribution. \doi{10.1109/RoboSoft54090.2022.9762226}

\item \myname, C.Majidi, ``Gaussian Process Dynamics Models for Soft Robots with Shape Memory Actuators.'' {\it IEEE International Conference on Soft Robotics (RoboSoft)}, April 2021.  \doi{10.1109/RoboSoft51838.2021.9479294}

\item Z. Patterson, \myname, K. Chin, T. Hellebrekers, C. Majidi, ``An Untethered Brittle Star Robot for Closed-Loop Underwater Locomotion.'' {\it IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS),} Oct. 2020. \doi{10.1109/IROS45743.2020.9341008}

\item L.H. Chen, M.C. Daly, \myname, L.A. Janse van Vuuren, H.J. Garnier, M.I. Verdugo, E. Tang, C.U. Spangenberg, F. Ghahani, A.K. Agogino, A.M. Agogino, ``Modular Elastic Lattice Platform for Rapid Prototyping of Tensegrity Robots.'' {\it  ASME International Design Engineering Technical Conferences (IDETC) / 41st Mechanisms and Robotics Conference}, Aug 2017. \doi{10.1115/DETC2017-68264}

\item \myname, A.K. Akella, Z.A. Ahmad, V. SunSpiral, ``Model-Predictive Control of a Flexible Spine Robot.'' {\it American Control Conference (ACC)}, IEEE, May 2017. \doi{10.23919/ACC.2017.7963738}

\item K. Zampaglione, \myname, L.H. Chen, A.M. Agogino,  A.K. Agogino, ``DNA-Structured Linear Actuators.'' {\it ASME International Design Engineering Technical Conferences (IDETC) / 40th Mechanisms and Robotics Conference}, Aug 2016. \doi{10.1115/DETC2016-60291}
  
\item \myname, H. Ji, P. Hylton, Y. Madaan, C. Yang, J. Friesen, V. SunSpiral, A.M. Agogino, ``Mechanism Design and Simulation of the ULTRA Spine, a Tensegrity Robot.'' {\it ASME International Design Engineering Technical Conferences (IDETC) / 39th Mechanisms and Robotics Conference}, Aug 2015. \doi{10.1115/DETC2015-47583}

\item \myname, J. Bruce, K. Caluwaerts, P. Manovi, R.F. Firoozi, S. Dobi, A.M. Agogino, V. SunSpiral, ``System Design and Locomotion of SUPERball, an Untethered Tensegrity Robot.'' {\it IEEE International Conference on Robotics and Automation (ICRA),} May 2015. \doi{10.1109/ICRA.2015.7139590}

\item \myname, J. Bruce, K. Caluwaerts, Y. Chen, D. Lu, Y. Liu, A.K. Agogino, V. SunSpiral, A.M. Agogino, ``Hardware Design and Testing of SUPERball, a Modular Tensegrity Robot.'' {\it The 6th World Conference on Structural Control and Monitoring (6WCSCM),} July 2014.

\item J. Bruce, \myname, Y. Chen, D.Lu, K. Morse, S. Milam, K. Caluwaerts, A.M. Agogino, V. SunSpiral, ``SUPERball: Exploring Tensegrities for Planetary Probes.'' {\it 12th International Symposium on Artificial Intelligence, Robotics, and Automation in Space (i-SAIRAS),} June 2014.

\item J. Bruce, K. Caluwaerts, A. Iscen, \myname, V. SunSpiral, ``Design and Evolution of a Modular Tensegrity Robot Platform.'' {\it IEEE International Conference on Robotics and Automation (ICRA),} May 2014. \doi{10.1109/ICRA.2014.6907361}

\item \myname, D. Mirsky, L.M. Hill, S. Bergbreiter, ``TinyTeRP: A Tiny Terrestrial Robotic Platform with Modular Sensing.'' {\it IEEE International Conference on Robotics and Automation (ICRA),} May 2013. \doi{ 10.1109/ICRA.2013.6630933}

\end{etaremune}

%\vspace{0.2cm}
%\section{Editorials}
%\vspace{0.2cm}

\vspace{0.2cm}
{\fontsubsection{Editorials}}
\vspace{0.2cm}

% For the publication titles, I use the 'description' font from the class.
\begin{etaremune}[itemsep=0.1cm]

\item X. Huang, \myname, M.K. Jawed, L. Jin, J. Zou, Y. Chen. ``Editorial: Materials, design, modeling and control of soft robotic artificial muscles.'' {\it Frontiers in Robotics and AI}, Nov. 2021.  \doi{10.3389/frobt.2022.1074549}

\end{etaremune}

%--------------------------------------------------------------------
% Workshop Publications (these went through peer review, but only by organizers.)
%--------------------------------------------------------------------

%%%%%%%%%%% AS OF JAN 3rd, 2020: No more workshop sections. These are all superseded by peer-reviewed publications, and I'm not always happy about the initial results in the workshops.

% \section{Workshop Publications}

% \vspace{0.2cm}

% \begin{etaremune}

% \item {\fontdescript{Inverse Kinematics for Control of Tensegrity Soft Robots: Existence and Optimality of Solutions.}} \underline{Sabelhaus, A.P.}; Agogino, A.K.; {\it IEEE/RSJ International Conference on Intelligent Robots and Systems: Workshop on Soft Robotic Modeling and Control,} Oct. 2018. Available, arXiv:1808.08252

% \item {\fontdescript{Trajectory Tracking Control of a Flexible Spine Robot, With and Without a Reference Input.}} \underline{Sabelhaus, A.P.}; Zhao, S.H.; Daly, M.C.; Tang, E.; Zhu, E.; Akella, A.K.; Ahmad, Z.A.; SunSpiral, V.; Agogino, A.M.; {\it NASA/ESA Conference on Adaptive Hardware and Systems: Structurally Adaptive Tensegrity Robots Workshop,} July 2017. Available, arXiv:1808.08309
  
% \end{etaremune}


% Do separate sections for under review (submitted, with preprints)
% and works-in-progress (no preprints)

%-----------------------------------------------------------------------
% Under review / works in progress
%------------------------------------------------------------------------

%\section{Under Review + Pre-prints}
%\vspace{0.2cm}


\vspace{0.2cm}
{\fontsubsection{Pre-prints and Under Review}}
\vspace{0.2cm}

\begin{etaremune}[itemsep=0.1cm]

\item \ranname, \mername, \juanname, \myname, ``Self-Sensing for Proprioception and Contact Detection in Soft Robots Using Shape Memory Alloy Artificial Muscles.'' {\it Preprint}. \arxiv{2409.17111}

\item \ranname, \mername, M. Ianus-Valdivia, A. Akber, C. Majidi, \myname, ``Safe Balancing Control of a Soft Legged Robot.'' {\it Preprint}. \arxiv{2209.13715}

\item \myname, L.A. Janse van Vuuren, A. Joshi, E. Zhu, H.J. Garnier, K.A. Sover, J. Navarro, A.K. Agogino, V. SunSpiral, A.M. Agogino, ``Design, Simulation, and Testing of a Flexible Actuated Spine for Quadruped Robots.'' {\it Preprint Only.} \arxiv{1804.06527}

%Available, arXiv:1804.06527 

\end{etaremune}  

%%%%%%%%%%
  
%\section{In-Preparation}

%\vspace{0.1cm}

%\begin{etaremune}[itemsep=0.1cm]

%\item \mername, \juanname, C. DeLorey, \ranname, S. Alizadeh-Shabdiz, Z. Patterson, \myname, ``Safe Autonomous Environmental Contact for Soft Robots using Control Barrier Functions.''

%\item \myname, L.A. Janse van Vuuren, D. Macri, A. Joshi, K.A. Sover, Z. Rodriquez, J. Navarro, A. Bronars, A.H. Li, A. Barkan, A. Zhang, A.K. Agogino, A.M. Agogino, ``Tensegrity Spines for Quadruped Robots.''

%\item \myname, ``Stability and Control Design for Lagrangian Systems with Statically-Conservative Forces.''

%\end{etaremune}

%-----------------------------------------------------
% Patents
%-----------------------------------------------------

%\section{Patents}
\vspace{0.2cm}
{\fontsubsection{Patents}}
\vspace{0.2cm}

\begin{etaremune}[itemsep=0.1cm]

\item A. Agogino, K. Zampaglione, L.-H. Chen, \myname, ``DNA Structured Linear Actuator.'' {\it US Patent No. 10,630,208}, issued April 21, 2020.

%\item L.-H. Chen, A. Agogino, M. Daly, \myname, A.K. Agogino, ``Elastic Lattices for Design of Tensegrity Structures and Robots.'' {\it Under review, US Patent Application No. US20190382995A1}.

\end{etaremune}


%-----------------------------------------------------
% External Service
%-----------------------------------------------------

\section{\underline{External Service}}
\vspace{0.2cm}

\begin{itemize}

\item {{\fontdescript{Editorial Work: Associate Editor} }
\vspace{0.1cm}
\begin{tightitemize}
\item {\it IEEE Robotics and Automation Letters (RA-L)}, 2025-present
\item {\it IEEE/RSJ International Conference on Intelligent Robots and Systems}, 2025
\item {\it IEEE International Conference on Soft Robotics (RoboSoft)}, 2025
\item {\it IEEE International Conference on Robotics and Automation (ICRA)}, 2022, 2023
\end{tightitemize}}

\item {{\fontdescript{Editorial Work: Guest Editor} }
\vspace{0.1cm}
\begin{tightitemize}
\item {\it Frontiers in Robotics and AI}: Special Topic on Materials, Design, Modeling and Control of Soft Robotic Artificial Muscles. 2022
\end{tightitemize}}

\item {{\fontdescript{Peer Review: Grants and Funding} }
\vspace{0.1cm}
\begin{tightitemize}
\item National Science Foundation (NSF), {\it Panel Reviewer, 2023, 2024}
\end{tightitemize}}

\item {{\fontdescript{Peer Review: Journals and Conferences} }
\vspace{0.1cm}
\begin{tightitemize}
\item Journals: {\it Soft Robotics, IEEE Robotics and Automation Letters (RA-L), International Journal of Robotics Research (IJRR), Science Robotics, Mechanism and Machine Theory, Acta Astronautica, IEEE Transactions on Control System Technology (T-CST), IEEE Transactions on Robotics (T-RO), Journal of Open-Source Software (JOSS), Frontiers in Robotics and AI, IEEE Robotics and Automation Magazine, International Journal of Space Structures (IJSS)}. 
\vspace{0.1cm}
\item Conferences: {\it  IEEE International Conference on Robotics and Automation (ICRA),  IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS),  American Control Conference (ACC), IEEE Conference on Decision and Control (CDC), IEEE International Conference on Soft Robotics (RoboSoft), IEEE RAS/EMBS International Conference on Biomedical Robotics \& Biomechatronics (BioRob), ASME International Design Engineering Technical Conference (IDETC), IEEE Conference on Control Technology and Applications (CCTA), IEEE/ASME Advanced Intelligent Mechatronics (AIM)}. 
\end{tightitemize}}

\end{itemize}

%-----------------------------------------------------
% Teaching
%-----------------------------------------------------

\section{\underline{Teaching}}
\vspace{0.2cm}

{\fontsubsection{At Boston University}}

\begin{etaremune}[itemsep=0.05cm]

\setcounter{enumi}{5}

\item {{\fontdescript{EK 103: Computational Linear Algebra,}} Boston University, Boston MA. S2022, S2023, S2024, S2025.}

\item {{\fontdescript{ME 500: Special Topics in Mechanical Engineering - Modeling of Motion in Mechanical Systems,}} Boston University, Boston MA. F2024.}

\item {{\fontdescript{EK 121: Introduction to Programming,}} Boston University, Boston MA. F2023.}

\end{etaremune}

\vspace{0.1cm}

{\fontsubsection{Before Joining Boston University}}

\begin{etaremune}[itemsep=0.05cm]

\item {{\fontdescript{Mech. Eng. 135/235: Design of Microprocessor-Based Mechanical Systems}}, Teaching Assistant, University of California Berkeley, Berkeley, CA. S2018.}

\end{etaremune}

%-----------------------------------------------------
% Mentorship and Supervision
%-----------------------------------------------------

\section{\underline{Mentorship and Supervision}}
\vspace{0.2cm}

{\fontsubsection{Visiting International Graduate Students - Boston University}}

\begin{etaremune}[itemsep=0.05cm]

\item Byungjun Kim, {\it Seoul National University}, 2024

\end{etaremune}

{\fontsubsection{PhD Students - Boston University}}

\vspace{0.2cm}

{\it All PhD students primarily advised by Sabelhaus. No co-advisors.}

\begin{etaremune}[itemsep=0.05cm]

\item Beibei Liu, {\it Systems Engineering}, 2024-present

\item Akua Dickson, {\it Systems Engineering}, 2023-present

\item Juan Pacheco Garcia, {\it Mechanical Engineering}, 2022-present

\item Ran Jing, {\it Mechanical Engineering}, 2022-present

\item Meredith Anderson, {\it Mechanical Engineering}, 2022-present

\end{etaremune}

{\fontsubsection{Master's Students - Boston University}}

\begin{etaremune}[itemsep=0.05cm]

\item Isara Cholaseuk, {\it M.S., Robotics and Autonomous Systems}, 2024-present

\item Guillermo Ao, {\it M.S., Robotics and Autonomous Systems}, 2023

\item Asbel Fontanez, {\it M.S., Robotics and Autonomous Systems}, 2022-2023

\item Amsal Ali Akber, {\it M.S., Robotics and Autonomous Systems}, 2022

\end{etaremune}

{\fontsubsection{Undergraduate Student Researchers - Boston University}}

\begin{etaremune}[itemsep=0.05cm]

\item Charles Van Hook, {\it B.S., Electrical Engineering}, 2024-present

\item Audrey Wang, {\it B.S., Mechanical Engineering}, 2024-present

\item Arnav Shah, {\it B.S., Electrical Engineering}, 2024

\item Susan Gamboa-Stumpf, {\it B.S., Mechanical Engineering}, 2024

\item Alvin Yang, {\it B.S., Mechanical Engineering}, 2023-present

\item Sarah Alizadeh-Shabdiz, {\it B.S., Mechanical Engineering}, 2023-present

\item Eileen Duong, {\it B.S., Mechanical Engineering}, 2022-2023

\item Miguel Ianus-Valdivia, {\it B.S., Mechanical Engineering}, 2022-2023

\end{etaremune}

% Just do selected/important invited talks.
%-----------------------------------------------------
% Invited Talks section.
%-----------------------------------------------------

\section{\underline{Invited Talks}}
\vspace{0.2cm}

{\fontsubsection{At Boston University}}

 \begin{etaremune}[itemsep=0.1cm]

\setcounter{enumi}{31}

\item ``Controlling Soft Robots: Safety, Autonomy, and Human Interaction.'' {\it Draper Labs}, Boston, MA. (Dec. 2024)

\item ``Challenges in Control and Autonomy for Soft Robots: Safety, Robustness, and Scalability.'' {\it University of Utah, Robotics Seminar}, Online. (Nov. 2023)

\item ``Challenges in Control Across Stiffness Scales: from Tensegrity to Softness.'' {\it IEEE/RSJ Intelligent Robots and Systems Conference (IROS) Tensegrity Robotics Workshop}, Detroit, MI. (Oct. 2023)

\item ``Challenges in Control and Autonomy for Soft Robots: Safety, Robustness, and Scalability.'' {\it Sekisui Chemical Co.}, Boston, MA. (July 2023)

\item ``Challenges in Control and Autonomy for Soft Robots: Safety, Robustness, and Scalability.'' {\it ASME International Design Engineering Technical Conferences (IDETC) Mechanisms and Robotics Special Early Career Session (SEC-sess)}, Boston, MA. (May 2023)

\item ``Challenges in Control and Autonomy for Soft Robots: Robustness, Scalability, and Safety.'' {\it Embodied Intelligence Conference}, Online. (Mar. 2023)

\item ``Controlling Soft Robots: Not as Hard as You'd Think.'' {\it Boston University Research On Tap}, Boston, MA. (Feb. 2023)

\item ``Controlling Soft Robots: Not as Hard as You'd Think.'' {\it University of Massachusetts Amherst, Department of Mechanical Engineering Seminar}, Amherst, MA. (Dec. 2022)

\item ``Safe Balancing Control of a Soft Legged Robot.'' {\it Northeast Regional Robotics Colloquium, Live Demonstrations}, Lowell, MA. (Oct. 2022)

\item ``Model-Predictive Control with Inverse Statics Optimization for Tensegrity Spine Robots.'' {\it IEEE Conference on Control Technology and Applications}, Trieste, Italy. (Aug. 2022)

\item ``Controlling Soft Robots: Not as Hard as You'd Think.'' {\it Applied Materials, Inc. Research Seminar Series}, Online. (July 2022)

\item ``Safe Supervisory Control of Soft Robot Actuators.'' {\it Robotics: Science and Systems, Workshop: The Science of Bumping Into Things, Towards Robots that Aren't Afraid of Contact}, New York, NY. (2022)

\item ``Close Enough is Good Enough: Approximations in Soft Robot Control.'' {\it Embodied Intelligence Conference}, Online. (Mar. 2022)


 \end{etaremune}

\vspace{0.2cm}

{\fontsubsection{Before Joining Boston University}}

\begin{etaremune}[itemsep=0.1cm]

\item ``Double-Helix Linear Actuators.'' {\it 4th ASME Journal of Mechanical Design Webinar, American Society of Mechanical Engineers}, Online. (Dec. 2021)

\item ``Soft Robot Locomotion: Not as Hard as You Might Think.'' {\it Intelligence Community Academic Research Syposium, United States Office of the Director of National Intelligence}, Online. (Sept. 2021)

\item ``Controlling Soft Robots: Not as Hard as You Might Think.'' {\it NGA IC Postdoc Speaker Series, National Geospatial Intelligence Agency}, Online. (June 2021)

\item ``Towards Rich Locomotion Gaits for Soft Robots.'' {\it CMU Locomotion Seminar, Carnegie Mellon University}, Pittsburgh, PA. (Nov. 2020)

\item  ``Gaussian Process Models for Soft Robot Locomotion." {\it Workshop on Application-Oriented Modeling and Control of Soft Robots, IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, Online. (Oct. 2020)

\item ``Tensegrity Spines for Quadruped Robots.'' {\it Workshop on Tensegrity Robotics, IEEE International Conference on Robotics and Automation (ICRA)}, Montreal, CA. (May 2019)

\item ``Tensegrity Spines for Quadruped Robots.'' {\it CMU Locomotion Seminar, Carnegie Mellon University}, Pittsburgh, PA. (Feb. 2019)

\item ``Model-Predictive Control for Tensegrity Spine Robots,'' {\it Stanford University, Autonomous Systems Lab}, Palo Alto, CA (Nov. 2018)

\item ``Laika and Belka: Walking Robots with Flexible Spines.'' {\it National Aeronautics and Space Administration, Workshop on Autonomy for Future NASA Science Missions}, Pittsburgh, PA. (Oct. 2018)

\item ``Inverse Kinematics for Tensegrity Soft Robot Control: Existence and Optimality.'' {\it Soft Robotics Modeling and Control Workshop, IEEE/RSJ International Conference on Intelligent Robots and Systems}, Madrid, Spain. (Oct. 2018)

\item ``Laika, The Four-Legged Robot with a Flexible Spine.'' {\it NASA Space Technology Day-On-The-Hill / United States Congress}, Washington, DC (Nov. 2017)

\item ``Laika, The Quadruped Robot with a Flexible Spine.'' {\it Bay Area Robotics Symposium (BARS)}, Palo Alto, CA (Oct. 2017)

\item ``Trajectory Tracking Control of a Flexible Spine Robot.'' {\it Workshop on Structurally Adaptive Tensegrity Robotics, 13th NASA/ESA Conference on Adaptive Hardware and Systems}, Los Angeles, CA (July 2017)

\item ``UC Berkeley Robotics for Disaster Relief.'' {\it Field Innovation Team Bootcamp 5.0}, Seattle, WA (Mar. 2017)

\item ``DNA-Structured Linear Actuators.'' {\it  SKTA Innopartners IP Redux}, Sunnyvale, CA (Apr. 2016)

\item ``The ULTRA Spine Project.'' {\it Bay Area Robotics Symposium (BARS)}, Berkeley, CA (Oct. 2015)

\item ``Robotics, Mechatronics, and Intelligent Systems.'' {\it Osher Lifelong Learning Institute}, Berkeley, CA (Feb. 2014)

 \end{etaremune}

\end{itemize}

%\vspace{0.1cm}

%Drew has served as a reviewer for the following journals and conferences:

%\vspace{0.4cm}
%
%\begin{tightitemize}
%
%\item Soft Robotics, 2021
%
%\item IEEE Robotics and Automation Letters (RA-L), 2017-2021
%
%\item IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS), 2018, 2020
%
%\item IEEE Transactions on Control System Technology (T-CST), 2018
%
%\item Journal of Open-Source Software (JOSS), 2018-2019
%  
%\item IEEE Robotics and Automation Magazine (RA-M), 2018
%  
%\item IEEE International Conference on Robotics and Automation (ICRA), 2017, 2019
%
%\item American Control Conference (ACC), 2017-2018.
%
%\item IEEE Conference on Control Technology and Applications (CCTA), 2017.
%
%\item International Journal of Space Structures, 2017.
%
%\item ASME International Design Engineering Technical Conference (IDETC), 2016-2017.
%
%\end{tightitemize}

%-----------------------------------------------------
% Teaching
%-----------------------------------------------------

\section{Teaching + Mentoring}

\vspace{0.2cm}

\begin{itemize}

\item {{\fontdescript{Mentorship of PhD students.}} 4 students. Diversity: 3/4 identify as minority or under-represented, 75\%.}

\item {{\fontdescript{Mentorship of master's students.}} 18 students. Diversity: 11/18 identify as minority or under-represented, 61\%.}

\item {{\fontdescript{Mentorship of undergraduate students.}} 22 students. Diversity: 14/22 identify as minority or under-represented, 64\%.}

\item {{\fontdescript{Instructor / Assistant Professor.}} Boston University.

\location{- Spring 2024 | Eng. 103, Computational Linear Algebra | Overall rating: --}

\location{- Fall 2023 | Eng. 121, Introduction to Programming | Overall rating: 3.26/5}
 
\location{- Spring 2023 | Eng. 103, Computational Linear Algebra | Overall rating: 4.63/5}

\location{- Spring 2022 | Eng. 103, Computational Linear Algebra | Overall rating: 4.54/5}}

\item {{\fontdescript{Graduate Student Instructor (GSI).}} University of California, Berkeley.

\location{- Spring 2018 | Mech. Eng. 135/235, Design of Microprocessor-Based Mechanical Systems}}

%\location{Spring 2022 | Eng. 103, Computational Linear Algebra}
%\vspace{0.1cm}
%\begin{tightitemize}
%\item Redesigned core freshman-level course in linear algebra with feasible and authentic content and assignments for engineering students
%\item Organized, lectured, graded, and assessed 95 students
%\item Course feedback and improvement underway.
%\end{tightitemize}}
%
%\item {{\fontdescript{Graduate Student Instructor (GSI).}} University of California, Berkeley.
% 
%\location{Spring 2018 | Mech. Eng. 135/235, Design of Microprocessor-Based Mechanical Systems}
%\vspace{0.1cm}
%\begin{tightitemize}
%\item Created course content for lab and discussion sections, delivered stand-in lectures, assisted students with projects.
%\item Overall Course Evaluations: {\it Total Effectiveness of Instructor: 4.7/5.0 (Undergrad.), 4.88/5.0 (Grad.)}
%\item Teaching evaluations were above department averages in every metric.
%\end{tightitemize}}

\item {{\fontdescript{Outstanding Graduate Student Instructor (GSI) Award.}} University of California, Berkeley, 2019}

% \location{Awarded upon nomination of students and department.}}

\end{itemize}

%\vspace{0.2cm}

%---------------------------------------------------------------------
% Diversity and Outreach
%---------------------------------------------------------------------

\section{Service + Outreach}

%\vspace{0.4cm}
\vspace{0.2cm}

%Professional organization and departmental service work:

\begin{itemize}

\item {\fontdescript{Service to the Mechanical Engineering Department at Boston University:}}

	\begin{tightitemize}
		\item Policies Task Force for Fostering Inclusive Environments, 2023
		\item PhD Fellowships Writing Group (Organizer), 2022-2023
	\end{tightitemize}

\item {\fontdescript{Service to the Systems Engineering Division at Boston University:}}

	\begin{tightitemize}
		\item Graduate Admissions Committee, 2022-2024
	\end{tightitemize}

\item \fontdescript{Faculty Advisor}. \fontlocation{Out in Science, Technology, Engineering, and Mathematics (oSTEM)$^\dag$ at Boston University, 2022 - present}

\item \fontdescript{Faculty/Staff Advisor}. \fontlocation{Out in Science, Technology, Engineering, and Mathematics (oSTEM)$^\dag$ at Carnegie Mellon University, 2020 - 2022.}

\item {\fontdescript{ASME Diversity and Inclusion Strategic Commitee (DISC), Advisor}.} American Society of Mechanical Engineers (ASME). Revised ASME policy P-15.11, PS16-02, and Statement on Diversity and Inclusion to include protections for transgender ASME members. June 2016 - 2018.

\item \fontdescript{ASEE LGBTQ Virtual Community of Practice, Member.} \fontlocation{American Society for Engineering Education. 2018 - 2020.}

\item {\fontdescript{Service to the Mechanical Engineering Department at UC Berkeley:}}

	\begin{tightitemize}
		\item Graduate Student Committee for Faculty Searches, 2017 - 2018.
		\item Graduate Peer Advisor for Equity, Diversity, and Inclusion Initiative, 2014 - 2015.
	\end{tightitemize}


%\item \fontdescript{Graduate Student Search Committee, Member.} \fontlocation{UC Berkeley Mechanical Engineering Faculty Searches. 2017 - 2018.}

%\item \fontdescript{Graduate Peer Advisor}. \fontlocation{UC Berkeley Mechanical Engineering - Equity, Diversity, and Inclusion Initiative. 2014 - 2015.}

\item \fontdescript{Coordinator, Chapter Leadership Programs}. \fontlocation{Out in Science, Technology, Engineering, and Mathematics$^\dag$ Incoporated. 2012 - 2013.}

\item {\fontdescript{Single Outreach Events (Selected):}}

	\begin{tightitemize}
		\item NASA Downlink Day with The Calculus Project, Boston University, 2022 and 2023: Demo and Lab Tour
		\item LGBTQ Professionals in STEM Panel, Boston University, 2022: Panelist
		\item NASA High School Camp at Carnegie Mellon University, 2021: Guest lecture
		\item Carnegie Science Center Day, 2020: Organized table presentation
		\item Cal Day, UC Berkeley, 2015-2019: Organized lab tours
		\item Robot Block Party, Silicon Valley Robotics, 2015, 2017: Organized table presentation
	\end{tightitemize}

\end{itemize}


%\vspace{-0.2cm}

% some explanations
%\hspace{1cm} {\small $^\dag$Out in Science, Technology, Engineering, and Mathematics (oSTEM) is a national organization for LGBTQ science and engineering students, \href{www.ostem.org}{www.ostem.org}}
{\small $^\dag$Out in Science, Technology, Engineering, and Mathematics (oSTEM) is a national organization for LGBTQ science and engineering students, \href{www.ostem.org}{www.ostem.org}}

%%%%%%%%%%%%%%%%%%%%%%%%%%

%Student organization service work:

%\begin{itemize}

%\item \fontdescript{Secondary Advisor}. \fontlocation{Out in Science, Technology, Engineering, and Mathematics (oSTEM) at UC Berkeley.  Berkeley, CA, Aug 2012 - April 2014.}

%\item \fontdescript{Founder and  Facilitator}. \fontlocation{Queer Council at the University of Maryland. College Park, MD, May 2011 - April 2012.}
  
%\item \fontdescript{Chapter President}. \fontlocation{Out in Science, Technology, Engineering, and Mathematics (oSTEM) at Maryland. College Park, MD, Nov 2010 - April 2012.}

%\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%

%Workshops presented:

%\begin{itemize}

%\item {\fontdescript{Facilitation Frameworks for LGBTQ College Students.}} Out in Science, Technology, Engineering, and Mathematics Incorporated (oSTEM) National Conference, Nov 2013.
  
%\item {\fontdescript{Topics in Queer Student Leadership: Assessment, Transitions, and Goal-Driven Planning.}} National Gay and Lesbian Task Force (NGLTF) Creating Change Conference, Jan 2013. Also presented at Midwest Bisexual, Lesbian, Gay, Transgender, and Allies College Conference (MBLGTACC), Feb 2013.
  
%\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%

\vspace{0.2cm}
\section{Professional development}
\vspace{0.2cm}

\begin{itemize}

\item {\fontdescript{Essentials of Effective Instruction.}} American Society for Engineering Education (ASEE). Intensive course on active learning and theory of teaching and learning for new instructors. Sept. 2021.

\item {\fontdescript{Summer Institute for Preparing Future Faculty.}} A professional development program to prepare students for academic careers. University of California, Berkeley. Completed / certified in June 2018.
  
\item {\fontdescript{Question, Persuade, Refer: Gatekeeper.}} Trained for response to mental health crises in students. University of California Berkeley Health Center, March 2018.

\item {\fontdescript{Teaching of Mechanical Engineering at the University Level.}} UC Berkeley Mechanical Engineering Department. Course on teaching pedagogy in engineering. Spring 2018.
  
\item {\fontdescript{Workshops on Teaching and Learning.}} UC Berkeley GSI Teaching and Resource Center / Academic Innovation Studio. Attended workshops on teaching pedagogy, including `How Students Learn' and `Teaming With Diversity.' Fall 2017 - Spring 2018.

\item {\fontdescript{Teaching Conference for Graduate Student Instructors.}} UC Berkeley GSI Teaching and Resource Center. Introductory pedagogy for first-time Graduate Student Instructors. Attended in Jan. 2018.

\end{itemize}


\sectionspace % Some whitespace after the section



\end{document}
