%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
% Drew Sabelhaus (apsabelhaus@berkeley.edu)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 

\begin{document}

%-------------------------------------------------------------------------
%	TITLE SECTION
%------------------------------------------------------------------------

\lastupdated % Print the Last Updated text at the top right

\raggedright{ % left-align the heading
\namesection{Drew (Andrew P.)}{Sabelhaus}{ % Your name
2807 Piedmont Ave, Berkeley CA 94705 \\
\urlstyle{same}\url{www.apsabelhaus.com} | 
\href{mailto:apsabelhaus@berkeley.edu}{apsabelhaus@berkeley.edu} | (301) 807-9842}
}

%--------------------------------------------------
% Page 1
%--------------------------------------------------



%--------------------------------------------------------------------------
%	LEFT COLUMN
%--------------------------------------------------------------------

\begin{minipage}[t]{0.33\textwidth}% The left column takes up 33% of the text width of the page

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education} 

\vspace{0.2cm}

\subsection{University of California, Berkeley}

\descript{PhD. Mechanical Engineering, Controls}
\location{Expected May 2017}

\sectionspace % Some whitespace after the section

\descript{MS. Mechanical Engineering, Controls}
\location{Expected Dec 2014}
\location{GPA: 3.85}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{University of Maryland}

\descript{B.S. Mechanical Engineering, Minor in Computer Science}
\location{May 2012 | College Park, MD}
\location{GPA: 3.7}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Skills
%------------------------------------------------

\section{Skills}

\vspace{0.2cm}

\subsection{Programming}

\location{Over 2000 lines:}
C \textbullet{} C++ \textbullet{} Linux Shell \\ 
MATLAB \textbullet{} Java \textbullet{} \LaTeX \\
\location{Over 500 lines:}
Python \textbullet{} Ruby \textbullet{} Assembly: ia32, MIPS \\
Visual Basic \textbullet{} nesC, TinyOS\\
\location{Familiar:}
OCaml \textbullet{} Julia \textbullet{} Android \textbullet{} Javascript \\
JSON \textbullet{} HTML \textbullet{} XML\\

\sectionspace

\subsection{Engineering Fabrication}

Surface-Mount PCB Layout and Assembly\\
Digital and Analog Circuit Design\\
Control System Design and Testing\\
Soldering \textbullet{} Machine Shop \textbullet{} Tolerancing\\


\sectionspace % Some whitespace after the section

\subsection{Honors, Awards}

NSF Graduate Research Fellowship, '12\\
Markowski-Leach Scholarship, '13-14\\
U.Md. Engineering Leadership Award, '12\\
U.Md. Presidential Scholarship, '08-12\\
L-3 Communications Scholarship, '11-12\\
U.Md. LGBT Equity Office Scholarship, '11\\
Thales Communications Scholarship, '10\\
Terex Corporation Scholarship, '09\\

%----------------------------------------------------------------------------

\end{minipage}% The end of the left column. Ensures no space.
\hfill
%
%----------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------
%

\begin{minipage}[t]{0.60\textwidth}% The right column takes up 66% of the text width of the page

%-----------------------------------------------------------------------
% Pubications
%------------------------------------------------------------------------

\section{Publications}

\vspace{0.4cm}

\begin{tightitemize}

\item \textbf{System Design and Locomotion of SUPERball, an Autonomous Tensegrity Robot.} Sabelhaus, A.P., Bruce, J., Caluwaerts, K., Manovi, P., Fallah Firoozi, R., Dobi, S., Agogino, A.M., SunSpiral, V., Submitted to International Conference on Robotics and Automation (ICRA), 2015

\item \textbf{Design and Control of Compliant Tensegrity Robots through Simulation and Hardware Validation.} Caluwaerts, K., Despraz, J., Iscen, A., Sabelhaus, A.P., Bruce, J., Schrauwen, B., SunSpiral, V.,  J. of the Royal Society Interface, Sept. 2014

\item \textbf{Hardware Design and Testing of SUPERball, a Modular Tensegrity Robot.} Sabelhaus, A.P., Bruce, J., Caluwaerts, K., Chen, Y., Lu, D., Liu, Y., Agogino, A.K., SunSpiral, V., Agogino, A.M., The 6th World Conference on Structural Control and Monitoring (6WCSM), July 2014

\item \textbf{SUPERball: Exploring Tensegrities for Planetary Probes.} Bruce, J., Sabelhaus, A.P., Chen, Y., Lu, D., Morse, K., Milam, S., Caluwaerts, K., Agogino, A.M., SunSpiral, V., 12th International Symposium on Artificial Intelligence, Robotics, and Automation in Space (i-SAIRAS), June 2014

\item \textbf{Design and Evolution of a Modular Tensegrity Robot Platform.} Bruce, J., Caluwaerts, K., Iscen, A., Sabelhaus, A.P., SunSpiral, V., International Conference on Robotics and Automation (ICRA), May 2014

\item \textbf{TinyTeRP: A Tiny Terrestrial Robotic Platform with Modular Sensing.} Sabelhaus, A.P., Mirsky, D., Hill, L.M., Bergbreiter, S., International Conference on Robotics and Automation (ICRA), May 2013 

\end{tightitemize}

\sectionspace

%-----------------------------------------------------
% Presentations, Workshops, and Posters section.
%-----------------------------------------------------

\section{Presentations, Workshops, Posters}

\vspace{0.4cm}
\begin{tightitemize}

\item \textbf{Robotics, Mechatronics, and Intelligent Systems.} Osher Lifelong Learning Institute,Feb 2014. Invited Talk.

\item \textbf{Fabulous Facilitation Frameworks for LGBTQ College Students.} Out in Science, Technology, Engineering, and Mathematics Incorporated (oSTEM) National Conference, Nov 2013. Workshop.

\item \textbf{Mechatronic Design of Tensegrity Robotic Systems for Dynamic Locomotion.} NASA Ames Research Center Autonomous Systems Lab Intern Poster Symposium, Aug 2013. Poster Session.

\item \textbf{TinyTeRP: A Tiny Terrestrial Robotic Platform with Modular Sensing.} International Conf. on Robotics and Automation (ICRA), May 2013. Presentation.

\item \textbf{Topics in Queer Student Leadership: Assessment, Transitions, and Goal-Driven Planning.} Midwest Bisexual, Gay, Lesbian, Transgender, and Allies College Conference, Feb 2013. Workshop.

\item \textbf{Topics in Queer Student Leadership: Assessment, Transitions, and Goal-Driven Planning.} National Gay and Lesbian Task Force Creating Change Conference, Jan 2013. Workshop.

\item \textbf{TinyTeRP: A Tiny Terrestrial Robotic Platform.} International Symposium on Distributed Autonomous Robotic Systems (DARS), Nov 2012. Poster Session.

\end{tightitemize}

%\sectionspace

%------------------------------------------------
% New page after publications, because I have a ton already
% Note that we have to do this in a minipage (ARGH) because of
% a weird ``unskip'' error if not.
%-----------------------------------------------

\end{minipage}% <- ensures no space at the end

\newpage % Start a new page

\begin{minipage}[t]{1\textwidth} % This minipage is the full width of the page.

%------------------------------------------------
% Research Experience
%------------------------------------------------

\section{Research Experience}

\vspace{0.4cm}

\runsubsection{Berkeley Emergent Space Technologies Lab (BEST)}
\descript{| Graduate Research Fellow}

\location{Sept 2012 - Present | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Led team of 5 master's students in designing and testing stuctural robotics components for a robot at NASA
\item Created new research program (the ``Tensegrity Spine Hardware Project''), recruited 5 master's students, led team on design and controls research
\item Recruited and mentored 2 undergraduate researchers
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{NASA Ames Research Center, Intelligent Robotics Group}
\descript{| Graduate Student Intern}

\location{Feb 2013 - Present | Moffett Field, CA}
\begin{tightitemize}
\item Mechanical design of SUPERball, an autonomous tensegrity robot: cable driving system, actuation system, active compliance spring system
\item Sensor design for SUPERball: designed, tested, calibrated, and assembled custom force gauges
\item Assisted in electronics design for SUPERball and programming in ROS (Robotic Operating System)
\item Wrote and maintained pieces of the NASA Tensegrity Robotics Toolkit in C++
\item Simulated different motions of SUPERball in NTRT, tested potential controls
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Maryland Microrobotics Lab}
\descript{| Undergraduate Researcher}

\location{Feb 2011 – Aug 2012 | College Park, MD}
\begin{tightitemize}
\item Designed circuit and PCB layout for 1.2 cm$^2$ mobile robot
\item Wrote data collection software and control algorithm for robot
\item Led team of 3 undergraduates and 1 REU student to a successful paper submission
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{U.S. Army Corps of Engineers Research Center}
\descript{| Mechanical Engineering Research Intern}

\location{Summer 2011 | Alexandria, VA}
\begin{tightitemize}
\item Researched and tested long-range wireless sensor network system
\item Wrote data collection software and management software for network nodes
\end{tightitemize}

\sectionspace

%------------------------------------------------
% Engineering Design Experience
%------------------------------------------------

\section{Other Engineering Design Experience}

\vspace{0.4cm}

%---------------------------------------------

\runsubsection{Soft Classification for Hybrid Systems using Gaussian Process Models}

\location{Spring 2014 | Hybrid Systems Identification and Control Course, UC Berkeley}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Researched Gaussian Process Models for Machine Learning, implemented software in MATLAB for regression over GPs

\item Developed innovative (to-be-published) algorithm for probabilistically classifying systems with online regression

\item Evaluated algorithm on simulated system (data from SUPERball simulation in NTRT)

\end{tightitemize}

\sectionspace % Some whitespace after the section

%---------------------------------------------

\runsubsection{Optimization-Based Control for an Underactuated Magnetic Levitation System}

\location{Fall 2013 | Advanced Robotics Course, UC Berkeley}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Designed a trajectory-tracking controller for a simplied model of an underactuated magnetic levitation system

\item Developed input-output linearized model for optimization initialization

\item Simulated and evaluated trajectory tracking performance for multiple disturbance modes

\end{tightitemize}

\sectionspace % Some whitespace after the section


%-----------------------------------------

\runsubsection{NearZero Design Project}
\descript{| Controls Group Lead}

\location{Spring 2013 | Advanced Design and Automation Course, UC Berkeley}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Designed sensing and actuation system for magnetically-levitated flywheel energy storage system

\item Formulated a Linear Quadratic Regulator controller, performed stability analysis of control system

\item Designed circuit and layout for 3 printed circuit boards for analog sensors, digital control, and electromagnet drivers

\end{tightitemize}

\sectionspace % Some whitespace after the section

%---------------------------------------------------------------------

\end{minipage} % The end of the right column

%---------------------------------------------------------------------
% Page 3: Leadership etc.
%---------------------------------------------------------------------

\newpage % Start a new page

\begin{minipage}[t]{1\textwidth} % this page is also full width

%------------------------------------------
% Soft stuff: leadership, outreach, ...
%-----------------------------------------

\section{Leadership, Outreach, and Organizational Work}

\vspace{0.4cm}

%------------------------------------------

\runsubsection{ Equity, Diversity, and Inclusion Initiative }
\descript{| Graduate Peer Advisor}

\location{Aug 2014 - Present | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item One of two graduate students spearheading diversity programs in the Mechanical Engineering Department at UC Berkeley

\item Held office hours, advised students on matters of inclusion, identity, research, and professional relationships

\item Organized lab tours for two high school groups from Santa Cruz, CA

\item Organized fellowship application draft reading team for under-represented students in the department

\item Currently planning and organizing large ``Engineering for All'' initiative for spring 2015

\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------

\runsubsection{ Out in Science, Technology, Engineering, and Mathematics Incoporated }
\descript{ Coordinator, Chapter Leadership Programs}

\location{July 2012 - Present | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Led data collection, programs assessment, and new programming efforts for national nonprofit organization serving LGBTQ students in STEM fields

\item Organized and led the Chapter Handbook Project team

\item Wrote 50+ pages of leadership instructional material for current oSTEM chapter leaders, edited other sections of the 80 page oSTEM Chapter Handbook (distributed Feb 2013)

\item Created online assessment strategy for handbook among student users

\item Created and presented unique skills workshops at national LGBTQ+ conferences

\item Temporarily filled open position on oSTEM Incorporated Board of Directors from late 2012 until mid 2013

\end{tightitemize}

\sectionspace % Some whitespace after the section

%---------------------------------------------------------

\runsubsection{ Out in Science, Technology, Engineering, and Mathematics at UC Berkeley}
\descript{ Secondary Advisor}

\location{Aug 2012 - Present | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Provided advice, training, and support to local oSTEM Chapter as a former leader

\item Mentored current and upcoming student leaders, in both personal and professional capacities

\item Assisted in leadership transitions and programs assessment

\end{tightitemize}

\sectionspace % Some whitespace after the section

%----------------------------------------------------------

\runsubsection{ Out in Science, Technology, Engineering, and Mathematics at Maryland}\\
\descript{Chapter President}

\location{Nov 2010 - April 2012 | College Park, MD}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Co-founded and led chapter of oSTEM at the University of Maryland, College Park

\item Wrote budgets for conference attendance and local events

\item Coordinated corporate sponsorships, totaling over \$3,000

\item Trained current group of student leaders for their leadership transition

\end{tightitemize}

\sectionspace % Some whitespace after the section

%-----------------------------------------------------

\runsubsection{ Queer Council at the University of Maryland}
\descript{ |  Founder, Facilitator}

\location{May 2011 - April 2012 | College Park, MD}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Founded organizational inter-group council for LGBTQ+ student group leaders at the University of Maryland

\item Led dialogue programs and generated cross-programming between groups

\item Facilitated discussions and advocated for the queer community to university staff and management

\end{tightitemize}

\sectionspace % Some whitespace after the section

\end{minipage}

%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

%\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page

%\section{Example Section}

%\end{minipage} % The end of the left column
%\hfill
%\begin{minipage}[t]{0.66\textwidth} % The right column takes up 66% of the text width of the page

%\section{Example Section 2}

%\end{minipage} % The end of the right column

%----------------------------------------------------------------------------------------

\end{document}
