%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
% This specific document released also under the same license,
% by Drew Sabelhaus.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[12pt,letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4 
%\thispagestyle{empty}

\usepackage[export]{adjustbox}

%%%%%%%%%% EXACT 1in MARGINS %%%%%%%                                   %%
\setlength{\textwidth}{6.5in}     %%                                   %%
\setlength{\oddsidemargin}{0in}   %% (It is recommended that you       %%
\setlength{\evensidemargin}{0in}  %%  not change these parameters,     %%
\setlength{\textheight}{8.5in}    %%  at the risk of having your       %%
\setlength{\topmargin}{0in}       %%  proposal dismissed on the basis  %%
\setlength{\headheight}{0in}      %%  of incorrect formatting!!!)      %%
\setlength{\headsep}{0in}         %%                                   %%
\setlength{\footskip}{.5in}       %%                                   %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

\begin{document}
\thispagestyle{empty}
%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

%\lastupdated % Print the Last Updated text at the top right

%\centering{ % left-align the heading
\underline{
\uppercase{Drew (Andrew P.) Sabelhaus | C.V. | www.apsabelhaus.com}
}\\
%}

\fussy
\vspace{-0.6cm}
%----------------------------------------------------------------------------------------
%	LEFT COLUMN
%----------------------------------------------------------------------------------------


\begin{minipage}[t][6.8in]{0.33\textwidth}% The left column takes up 33% of the text width of the page
%\vspace{0.2cm}
%------------------------------------------------
% Education
%------------------------------------------------
\section{\underline{Education} }

\vspace{0.2cm}

\subsection{\textbf{University of California, Berkeley}}

\descript{PhD. Mechanical Engineering, Controls}
\location{Expected May 2017}

\sectionspace % Some whitespace after the section

\descript{MS. Mechanical Engineering, Controls}
\location{Expected Dec 2014}
\location{GPA: 3.78}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\subsection{\textbf{University of Maryland}}

\descript{B.S. Mechanical Engineering, Minor in Computer Science}
\location{May 2012 | College Park, MD}
\location{GPA: 3.69}

\sectionspace % Some whitespace after the section

\section{\underline{Honors, Awards}}

\vspace{0.2cm}

%\begin{tightitemize}

%\item NSF Graduate Research Fellowship, 2012-Present\\

%\item Markowski-Leach Scholarhip, 2013-Present\\

%\end{tightitemize}
\textbullet{} NSF Graduate Research\\ \quad Fellowship, 2012-Present\\
\vspace{0.1cm}

\textbullet{} Markowski-Leach\\ \quad Scholarship, 2013-Present\\
\vspace{0.1cm}

\textbullet{} University of Maryland\\ \quad Engineering Leadership\\ \quad Award, 2012\\
\vspace{0.1cm}

\textbullet{} University of Maryland\\ \quad Presidential Scholarship,\\ \quad 2008-2012\\
\vspace{0.1cm}

\textbullet{} L-3 Communications\\ \quad Scholarship, 2011-2012\\
\vspace{0.1cm}

\textbullet{} University of Maryland\\ \quad Office of LGBT Equity\\ \quad Scholarship, 2011\\
\vspace{0.1cm}

\textbullet{} Thales Communications\\ \quad Scholarship, 2010\\
\vspace{0.1cm}

\textbullet{} Terex Corporation\\ \quad Scholarship, 2009\\

%----------------------------------------------------------------------------
\end{minipage}% The end of the left column. Ensures no space.
\hfill
%
%----------------------------------------------------------------------------
%	RIGHT COLUMN
%----------------------------------------------------------------------------
%
%\raggedright{
\hspace{-3in}
\begin{minipage}[t][6.8in][t]{0.66\textwidth}% The right column takes up 66% of the text width of the page
%\begin{minipage}[t][7in]{0.66\textwidth}% The right column takes up 66% of the text width of the page
%-----------------------------------------------------------------------
% Pubications
%------------------------------------------------------------------------
\raggedright{

\hspace{-2in}

\section{\quad \underline{Publications}}

\vspace{0.4cm}

\begin{tightitemize}

\item \textbf{System Design and Locomotion of SUPERball, an Autonomous Tensegrity Robot.} Sabelhaus, A.P. et al. Submitted to International Conference on Robotics \\and Automation (ICRA) 2015

\item \textbf{Design and Control of Compliant Tensegrity Robots through Simulation and Hardware Validation.} Caluwaerts, K., ... Sabelhaus, A.P. et al. Journal of the Royal Society Interface 2014

\item \textbf{Hardware Design and Testing of SUPERball, a Modular Tensegrity Robot.} Sabelhaus, A.P. et al. The 6th World Conference on Structural Control and Monitoring (6WCSM) 2014

\item \textbf{SUPERball: Exploring Tensegrities for Planetary Probes.} Bruce, J., Sabelhaus, A.P. et al. 12th International Symposium on Artificial Intelligence, Robotics, and Automation in Space (i-SAIRAS) 2014

\item \textbf{Design and Evolution of a Modular Tensegrity Robot Platform.} Bruce, J., ...Sabelhaus, A.P. et al. International Conference on Robotics and Automation (ICRA) 2014

\item \textbf{TinyTeRP: A Tiny Terrestrial Robotic Platform with Modular Sensing.} Sabelhaus, A.P. et al. International Conference on Robotics and Automation (ICRA) 2013 

\end{tightitemize}

\sectionspace

%-----------------------------------------------------
% Presentations, Workshops, and Posters section.
%-----------------------------------------------------

\section{\quad \underline{Presentations, Workshops, Posters}}

\vspace{0.4cm}
\begin{tightitemize}

\item \textbf{Mechatronic Design of Tensegrity Robotic Systems for Dynamic Locomotion.} NASA Ames Research Center Autonomous Systems Lab Intern Poster Symposium, Aug 2013. Poster Session.

\item \textbf{TinyTeRP: A Tiny Terrestrial Robotic Platform with Modular Sensing.} International Conf. on Robotics and Automation (ICRA), May 2013. Presentation.

\item \textbf{TinyTeRP: A Tiny Terrestrial Robotic Platform.} International Symposium on Distributed Autonomous Robotic Systems (DARS), Nov 2012. Poster Session.

\end{tightitemize}

%\sectionspace

%------------------------------------------------
% New page after publications, because I have a ton already
% Note that we have to do this in a minipage (ARGH) because of
% a weird ``unskip'' error if not.
%-----------------------------------------------
}
\end{minipage}% <- ensures no space at the end
%}

\vspace{0.45cm}

\raggedright{
\quad \underline{OUTREACH, LEADERSHIP}\\

\begin{tightitemize}

\item \textbf{Graduate Peer Advisor}. Equity, Diversity, and Inclusion Initiative in the Mechanical Engineering Department at UC Berkeley. Aug 2014 - Present.

\item \textbf{Coordinator, Chapter Leadership Programs}. Out in Science, Technology, Engineering, and Mathematics (oSTEM) Incorporated. July 2012 - Present.

\item \textbf{President, Co-Founder}. oSTEM at the University of Maryland. Nov 2010 - Apr 2012.

\end{tightitemize}
%Here is some new text.
%This is the same paragraph.\\
%This is a new paragraph.
}
\newpage % Start a new page
\thispagestyle{empty}
\begin{minipage}[t]{1\textwidth}% This minipage is the full width of the page.
%------------------------------------------------
% Research Experience
%------------------------------------------------
\section{\underline{Research Experience}}

\vspace{0.2cm}

\runsubsection{Berkeley Emergent Space Technologies Lab (BEST)}
\descript{| Graduate Research Fellow}

\location{Sept 2012 - Present | Berkeley, CA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}
\item Led team of 5 master's students in designing and testing stuctural robotics components
\item Created new research program (the ``Tensegrity Spine Hardware Project''), recruited 5 master's students, led team on design and controls research
\item Recruited and mentored 2 undergraduate researchers
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{NASA Ames Research Center, Intelligent Robotics Group}
\descript{| Graduate Student Intern}

\location{Feb 2013 - Present | Moffett Field, CA}
\begin{tightitemize}
\item Mechanical design of SUPERball, an autonomous tensegrity robot: cable driving system, actuation system, active compliance spring system
\item Sensor design for SUPERball: fabricated, tested, and calibrated, custom force gauges
\item Assisted in electronics design for SUPERball and programming in ROS (Robotic OS)
\item Wrote and maintained pieces of the NASA Tensegrity Robotics Toolkit (NTRT) in C++
\item Simulated different motions of SUPERball in NTRT, tested potential controls
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{Maryland Microrobotics Lab}
\descript{| Undergraduate Researcher}

\location{Feb 2011 – Aug 2012 | College Park, MD}
\begin{tightitemize}
\item Designed circuit and PCB layout for 1.2 cm$^2$ mobile robot
\item Wrote data collection software and control algorithm for robot
\item Led team of 3 undergraduates and 1 REU student to a successful paper submission
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------

\runsubsection{U.S. Army Corps of Engineers Research Center}
\descript{| Mechanical Engineering Research Intern}

\location{Summer 2011 | Alexandria, VA}
\begin{tightitemize}
\item Researched and tested long-range wireless sensor network system
\item Wrote data collection software and management software for network nodes
\end{tightitemize}

\sectionspace

%------------------------------------------------
% Engineering Design Experience
%------------------------------------------------

\section{\underline{Other Engineering Design Experience}}

\vspace{0.2cm}

%---------------------------------------------

\runsubsection{Soft Classification for Hybrid Systems using Gaussian Process Models}

\location{Spring 2014 | Hybrid Systems Identification and Control Course, UC Berkeley}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Researched Gaussian Process Models for Machine Learning, implemented software in MATLAB and Python for regression over GPs

\item Developed innovative (to-be-published) algorithm for probabilistically classifying systems with online regression

\item Evaluated algorithm on simulated system (data from SUPERball simulation in NTRT)

\end{tightitemize}

\sectionspace

\runsubsection{Optimization-Based Control for an Underactuated Magnetic Levitation System}

\location{Fall 2013 | Advanced Robotics Course, UC Berkeley}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Designed a sequential quadratic programming trajectory-tracking controller for a simplied model of an underactuated magnetic levitation system

\item Developed input-output nonlinear system transform for optimization initialization

\item Simulated and evaluated trajectory tracking performance for disturbances

\end{tightitemize}

\sectionspace % Some whitespace after the section

%-----------------------------------------

\runsubsection{NearZero Design Project}
\descript{| Controls Group Lead}

\location{Spring 2013 | Advanced Design and Automation Course, UC Berkeley}
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightitemize}

\item Designed sensing and actuation system (3 PCBs, digital and analog) for magnetically-levitated flywheel energy storage system

\item Formulated a LQR controller, performed stability analysis of control system

\end{tightitemize}

\sectionspace % Some whitespace after the section

%---------------------------------------------------------------------
\end{minipage} % The end of the right column

\end{document}
